Asteroseismology of GD358 with complex C/O core profiles

### 2016-02-11 msnew.tex
housekeeping

\author {Agn\`es~Bischoff-Kim\altaffilmark{1},
J.~L. Provencal\altaffilmark{2,3},
M.~H.~Montgomery\altaffilmark{3,4},
Samuel~T.~Harrold\altaffilmark{4},
B.~Howard\altaffilmark{3},
W.~Strickland\altaffilmark{5},
D.~Chandler\altaffilmark{5},
D.~Campbell\altaffilmark{5},
A.~Arredondo\altaffilmark{5},
R.~Linn\altaffilmark{5},
D.~P.~Russell\altaffilmark{5},
D.~Doyle\altaffilmark{5},
A.~Brickhouse\altaffilmark{5},
R.~Linn\altaffilmark{5},
D.~Peters\altaffilmark{5},
A.~V.~Kusakin\altaffilmark{6},
A.~V.~Sergeev\altaffilmark{7},
M.~Andreev\altaffilmark{7},
A.~Maksim\altaffilmark{7},
S. Velichko\altaffilmark{7}
R.~Janulis\altaffilmark{8},
F.~Ali\c cavu\c s\altaffilmark{9},
N. Horoz\altaffilmark{9},
S.~Zola\altaffilmark{10,11},
W.~Og{\l}oza\altaffilmark{10,11},
D.~Koziel-Wierzbowska{10,11},
T.~Kundera\altaffilmark{10,11},
D. Jableka\altaffilmark{10,11},
B. Debski\altaffilmark{10,11},
S. Meingast\altaffilmark{12},
}
\altaffiltext{1}{Penn State Worthington Scranton, Dunmore, PA 18512; axk55@psu.edu}
\altaffiltext{2}{University of Delaware, Department of Physics and Astronomy
Newark, DE 19716; jlp@udel.edu}
\altaffiltext{3}{Delaware Asteroseismic Research Center, Mt. Cuba Observatory,
Greenville, DE 19807}
\altaffiltext{4}{Department of Astronomy, University of Texas, Austin, TX 78712;
mikemon@rocky.as.utexas.edu}
\altaffiltext{5}{Meyer Observatory and Central Texas Astronomical Society, 209
Paintbrush, Waco, TX 76705; chandler@vvm.com}
\altaffiltext{6}{Fesenkov Astrophysical Institute, Almaty 050020, Kazakhstan}
\altaffiltext{7}{Ukrainian National Academy of Sciences, Main Astronomical
Observatory, Golosiiv, Kiev 022 252650; sergeev@terskol.com }
\altaffiltext{8}{Institute of Theoretical Physics and Astronomy, Vilnius
University, Vilnius, Lithuania; jr@itpa.lt}
\altaffiltext{9}{Ulupinar Observatory, \c Canakkale Onsekiz Mart University, Turkey}
\altaffiltext{10}{Astronomical Observatory of the Jagiellonian University, ul. Orla
171, 30-244 Cracow, Poland; szola@oa.uj.edu.pl}
\altaffiltext{11}{Mount Suhora Observatory, Cracow Pedagogical University, Ul.
Podchorazych 2, 30-084 Krakow, Poland; zola@astro1.as.ap.krakow.pl}
\altaffiltext{12}{Institut f\H ur Astrophysik, Universit\H at Wien, T\H urkenschanzstrasse 17, 1180 Wien, Austria}

@@

The subject of this paper, GD358 (V777 Her) is the brightest ($m_{\rm v}=13.7$) and best 
studied helium atmosphere white dwarf pulsator. It is located near the red edge of the 
instability strip (\teff = , \logg =). GD358's pulsation spectrum contains a series of 
independent modes, many with complex multiplet structure.  Models involving magnetic 
fields have been proposed to explain that structure \citep{Montgomery10}. Of importance for
this work is the fact that the spacing of the multiplets is consistent with theoretical 
predictions for a series of $l=1$ modes \citep{Provencal09}.

@@

We present a new detailed asteroseismic analysis of GD358, taking advantage of 
its long sequence of $\ell=1$ modes to better constrain the asteroseismic fits and 
define the limits of high precision white dwarf asteroseismology.  Our goals are two-fold.  
First, we will incorporate advanced asteroseismic models to explore parameter space 
\citet{BischoffKim14}. For example, the even period spacing observed in GD358's 
pulsation spectrum is consistent with the theory of g-mode non-radial pulsations. The 
magnitude of the spacing is expected to be related to how compressible the stellar 
interior is. The compressibility of the interior should be inversely proportional to the 
effective temperature. A hotter object would be less compact. On the other hand, a more 
massive model will have a higher density and be less compressible. These properties lead 
to distinguishable features of the models in the mass versus effective temperature 
parameter plane. We can explore such features with GD358 because we have a long, 
confirmed, single $\ell$ sequence of modes of higher radial order.

@@

In Section \ref{data}, we present our new observations and outline the data reduction process.  
In Section \ref{freq}, we establish the framework for frequency identification, and present the 
list of frequencies used for the asteroseismic investigation.  Section \ref{aster} outlines the 
asteroseismic investigation, and .....

@@

Standard procedure for WET observations calls for observers to transfer raw images and 
calibration files to WET headquarters for analysis at the end of each local night. CCD 
data reduction follows the steps described in \citet{Provencal12}. In brief, the new observations 
were obtained with different CCD photometers, each with distinct effective bandpasses. 
We minimize the bandpass issues by using CCDs with similar detectors whenever possible and 
employing a red cutoff filter (BG40 or S8612) to normalize wavelength response and 
reduce extinction effects. We corrected each image for bias and thermal noise, and 
normalized by the flat field. Aperture photometry using the Maestro photometry pipeline 
described by \citet{Dalessio10} was performed on each image, utilizing a range of 
aperture sizes for the target and comparison stars. For each individual nightly run, we 
chose the combination of aperture size and comparison star(s) producing the highest 
signal/noise light curve.

We used the WQED pipeline \citet{wqed} to examine each nightly light curve for photometric 
quality, remove outlying points, divide by suitable comparison stars, and correct for 
differential extinction. Our observational technique is therefore not sensitive to 
oscillations longer than a few hours. The result is a series of light curves 
with amplitude variations represented as fractional intensity (mmi). The unit is a linear 
representation of the fractional intensity of modulation (1 mmi $\approx$1 mmag). We present
our Fourier transforms (FTs) in units of modulation amplitude 
($1\sim mma=1 \times 10^{-3} {\rm ma} = 0.1 \% = 1\sim ppt$).

@@

\begin{figure}
\plotone{gd358multidft}
\caption{Fourier Transforms of GD358 for the 2010, 2011, and 2014 observing seasons.
The frequency range of the observed series of $\ell=1$ modes discussed in Section \ref{analysis} 
is indicated by the left arrow (red).  Peaks below $\approx$ 2400 \muHz are combination 
frequencies discussed in Section \ref{analysis} (right arrow, blue). 
(A color version of this figure is available in the online journal.)
\label{fts}
}
\end{figure}

@@

Perusal of Tables \ref{freq1} and \ref{freq2} shows that GD358's observed frequencies vary in two
important ways.  First, frequencies detected in a given observing season are not found 
in all observing seasons. Asteroseismology is based on the assumption that the available pulsation
frequencies are linked to stellar structure.  Since we are fairly certain that GD358's internal structure 
does not change on the timescales of the observations, we can assume that GD358 excites 
different subsets of its available pulsations at different times. While this is a common phenomenon
seen in white dwarf pulsators, the selection mechanism remains mysterious. The best way to 
determine GD358's complete set of pulsation frequencies is to combine frequency identifications 
from multiple observing seasons as outlined in \citep{Kleinman98}.

\begin{figure}
\epsscale{0.8}
%\plottwo{gd358multif_2015.eps}{gd358multi.eps}
%\centering{
%\includegraphics[width=1.0]{gd358multif_2015.eps}
%}
\plotone{gd358multif_2015.eps}
\caption{A schematic representation of GD358's pulsation modes for all available data between
1982 and 2015. Systematic patterns of distribution are evident. The bands between 2400 and 1000
\muHz (400 and 1000 s) are of particular importance for this work. (A color version of this 
figure is available in the online journal.)
\label{schematic}
}
\end{figure}

Figure~\ref{schematic} presents a schematic representation of GD358's pulsation frequencies for all the 
available data. The features of asteroseismic importance are the localized bands between 900 and 2400
\muHz (1100 and 400 s). We interpret each band to represent a single radial overtone in GD358. The bands
themselves illustrate the second way in which GD358's frequencies vary. Each band consists of 
frequency detections from multiple observing seasons, but each band is significantly wider in 
frequency space than the frequency error of any single measurement, arguing that some process 
is acting on the frequencies. The simplest explanation is rotational splitting.  However, with the 
exception of the two highest frequency (shortest period) bands ($k=8$ and $k=9$ 
from \citet{Provencal09}), we find no clear evidence of multiplet structure in the frequency 
distributions of the lower frequency (longer period) bands. The lower frequency band widths are 
most likely the result of amplitude and/or frequency modulation that obscures any underlying 
signatures of rotational splitting.

\begin{figure}
 \epsscale{1.0}
 \plotone{gd358k17_k8.eps}
% \plottwo{gd358multifk17.eps}{gd358multifk8.eps}
 \caption{The detailed schematic distribution of frequencies for the bands near 1300 {\em{right}}
 and 2360 \muHz {\em{left}}. The 1300 \muHz band shows no multiplet structure, unlike the 2360 \muHz
 band. Here we see clear evidence of multiplet structure. Assuming the triplet structure represents
 $l=1$, this implies a rotation period of $\approx 1.5$ days. Note changes in the scale for both axes.
 (A color version of this figure is available in the online journal.)
 \label{rot}}
\end{figure}

Figure \ref{schematic} also shows that the widths of the bands is not constant, but changes from band to band.
\citet{Bell15} presents an interesting analysis of the hydrogen atmosphere pulsator (DAV) \kicnsp 4552982, 
in which they identify 17 bands of pulsation frequencies. This DAV follows the general pattern exhibited 
by GD358: the highest frequency (shortest period) mode shows evidence of rotational splitting, while the 
lower frequency (longer period) modes are complex bands. The authors note that this DAV's bands have 
different widths in frequency space, and that there may be astronomical significance to this. Although the 
observational timebases are quite different (20 months for \kicnsp 4552982 vs 30 years for GD358), our 
data presents the opportunity to investigate this for a DB pulsator.  We measured the width of each of 
GD358's band. We define ''width'' as the difference between the lowest and highest frequency 
detected in each band. Figure \ref{thick} presents the results. The widths of GD358's bands are 
commensurate with those found in \kicnsp 4552982.  We also find a general increase in width with 
decreasing frequency (increasing period), until we reach the mode at 1238\muHz (807 s). This band has 
a width at least twice as wide as any other.  What is different about this mode???

@@

GD358's combination frequencies provide a tool by which we can bolster $l$ identifications. 
Combination frequencies are typically observed in the FTs of moderate to large amplitude pulsators.  
They are identified by their exact numerical relationships with parent frequencies.  
The combinations themselves are not independent, but result from nonlinear effects associated 
with the surface convection zone \citep{Brickhill92, Brassard95, Wu01, Ising01}.  
\citet{Wu01} lays the groundwork, showing that observed amplitudes of the combination 
frequencies depend on geometric factors such as the $(l,m)$ indices of the parents and the 
inclination of the pulsation axis to the line of sight.

@@

Figure~\ref{amps} shows the resulting probability distribution of $l$ and $m$ values for the 1735.96 \muHz
frequency detected in 2014.

\begin{figure}
 \epsscale{0.8}
 \plotone{modeamps.eps}
 \caption{Probability distribution (from 0 to 1) of $l$ and $m$ values for the 1735.96 variation detected in 
 2014.  The solutions are from individual simulations with $Res_{rms}<9.5e-06$. The amplitudes of the 
 observed combination frequencies argue that this is $l$=1, $m$=1.  
 \label{modeamps}
 }
\end{figure}

@@

\section{Asteroseismic fitting}\ref{astero}
\label{fitting}

@@

\input{gd358fit.tex} % label is gd358freq

@@

\begin{deluxetable}{rrrrr}
\tablecolumns{5}
\tabletypesize{\small}
\tablewidth{0pc}
\tablecaption{}
\tablehead{
\colhead{Run Name} & \colhead{Telescope} & \colhead{Detector} & \colhead{Date} & \colhead{Length}\\
\colhead{} & \colhead{} & \colhead{} & \colhead{} & \colhead{(hrs)}
\label{journal}}
\startdata
%\input{journaldata.tex}
\enddata
\end{deluxetable}

@@

%\input{1982freq.tex}
\clearpage
%\input{2011freq.tex}
\clearpage
\clearpage
\input{fitt1} % label is fitt1
\clearpage
%\begin{thebibliography}{}
%\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi

>>>>

\author {Agn\`es~Bischoff-Kim\altaffilmark{1},
J.~L. Provencal\altaffilmark{2,3},
M.~H.~Montgomery\altaffilmark{3,4},
Samuel~T.~Harrold\altaffilmark{4},
B.~Howard\altaffilmark{3},
W.~Strickland\altaffilmark{5},
D.~Chandler\altaffilmark{5},
D.~Campbell\altaffilmark{5},
A.~Arredondo\altaffilmark{5},
R.~Linn\altaffilmark{5},
D.~P.~Russell\altaffilmark{5},
D.~Doyle\altaffilmark{5},
A.~Brickhouse\altaffilmark{5},
R.~Linn\altaffilmark{5},
D.~Peters\altaffilmark{5},
A.~V.~Kusakin\altaffilmark{6},
A.~V.~Sergeev\altaffilmark{7},
M.~Andreev\altaffilmark{7},
A.~Maksim\altaffilmark{7},
S. Velichko\altaffilmark{7}
R.~Janulis\altaffilmark{8},
F.~Ali\c cavu\c s\altaffilmark{9},
N. Horoz\altaffilmark{9},
S.~Zola\altaffilmark{10,11},
W.~Og{\l}oza\altaffilmark{10,11},
D.~Koziel-Wierzbowska{10,11},
T.~Kundera\altaffilmark{10,11},
D. Jableka\altaffilmark{10,11},
B. Debski\altaffilmark{10,11},
S. Meingast\altaffilmark{12}
}
\altaffiltext{1}{Penn State Worthington Scranton, Dunmore, PA 18512; axk55@psu.edu}
\altaffiltext{2}{University of Delaware, Department of Physics and Astronomy
Newark, DE 19716; jlp@udel.edu}
\altaffiltext{3}{Delaware Asteroseismic Research Center, Mt. Cuba Observatory,
Greenville, DE 19807}
\altaffiltext{4}{Department of Astronomy, University of Texas, Austin, TX 78712;
mikemon@rocky.as.utexas.edu}
\altaffiltext{5}{Meyer Observatory and Central Texas Astronomical Society, 209
Paintbrush, Waco, TX 76705; chandler@vvm.com}
\altaffiltext{6}{Fesenkov Astrophysical Institute, Almaty 050020, Kazakhstan}
\altaffiltext{7}{Ukrainian National Academy of Sciences, Main Astronomical
Observatory, Golosiiv, Kiev 022 252650; sergeev@terskol.com }
\altaffiltext{8}{Institute of Theoretical Physics and Astronomy, Vilnius
University, Vilnius, Lithuania; jr@itpa.lt}
\altaffiltext{9}{Ulupinar Observatory, \c Canakkale Onsekiz Mart University, Turkey}
\altaffiltext{10}{Astronomical Observatory of the Jagiellonian University, ul. Orla
171, 30-244 Cracow, Poland; szola@oa.uj.edu.pl}
\altaffiltext{11}{Mount Suhora Observatory, Cracow Pedagogical University, Ul.
Podchorazych 2, 30-084 Krakow, Poland; zola@astro1.as.ap.krakow.pl}
\altaffiltext{12}{Institut f\H ur Astrophysik, Universit\H at Wien, T\H urkenschanzstrasse 17, 1180 Wien, Austria}

@@

The subject of this paper, GD358 (V777 Her) is the brightest ($m_{\rm v}=13.7$) and best 
studied helium atmosphere white dwarf pulsator. It is located near the red edge of the 
instability strip, with \teff of 24000~K and \logg of 7.8 \citep{Koester2013}. GD358's 
pulsation spectrum contains a series of independent modes, many with complex 
frequency structure.  Models involving magnetic fields and oblique rotation have been 
proposed to explain that structure \citep{Montgomery10}. Of importance for
this work is the fact that the spacing of the multiplets is consistent with theoretical 
predictions for a series of $\ell=1$ modes \citep{Provencal09}.

@@

We present a new detailed asteroseismic analysis of GD358, taking advantage of 
its long sequence of $\ell=1$ modes to better constrain the asteroseismic fits and 
define the limits of high precision white dwarf asteroseismology.  Our goals are two-fold.  
First, we will incorporate advanced asteroseismic models to explore parameter space 
\citep{BischoffKim14}. For example, the even period spacing observed in GD358's 
pulsation spectrum is consistent with the theory of g-mode non-radial pulsations. The 
magnitude of the spacing is expected to be related to how compressible the stellar 
interior is. The compressibility of the interior should be inversely proportional to the 
effective temperature. A hotter object would be less compact. On the other hand, a more 
massive model will have a higher density and be less compressible. These properties lead 
to distinguishable features of the models in the mass versus effective temperature 
parameter plane. We can explore such features with GD358 because we have a long, 
confirmed, single $\ell$ sequence of modes of higher radial order.

@@

In Section \ref{data}, we present our new observations and outline the data reduction process.  
In Section \ref{freq}, we establish the framework for frequency identification, and present the 
list of frequencies used for the asteroseismic investigation.  Section \ref{fitting} outlines the 
asteroseismic investigation, and .....

@@

Standard WET procedure calls for observers to transfer raw images and 
calibration files to WET headquarters for analysis at the end of each local night. CCD 
data reduction follows the steps described in \citet{Provencal12}. In brief, the new observations 
were obtained with different CCD photometers, each with distinct effective bandpasses. 
We minimize the bandpass issues by using CCDs with similar detectors whenever possible and 
employing a red cutoff filter (BG40 or S8612) to normalize wavelength response and 
reduce extinction effects. We corrected each image for bias and thermal noise, and 
normalized by the flat field. Aperture photometry using the Maestro photometry pipeline 
described by \citet{Dalessio10} was performed on each image, utilizing a range of 
aperture sizes for the target and comparison stars. For each individual nightly run, we 
chose the combination of aperture size and comparison star(s) producing the highest 
signal/noise light curve.

We used the WQED pipeline \citep{wqed} to examine each nightly light curve for photometric 
quality, remove outlying points, divide by suitable comparison stars, and correct for 
differential extinction. Our observational technique is therefore not sensitive to 
oscillations longer than a few hours. The result is a series of light curves 
with amplitude variations represented as fractional intensity (mmi). The unit is a linear 
representation of the fractional intensity of modulation (1 mmi $\approx$1 mmag). We present
our Fourier transforms (FTs) in units of modulation amplitude 
($1\sim mma=1 \times 10^{-3} {\rm ma} = 0.1 \% = 1\sim ppt$).

@@

\begin{figure}
\plotone{gd358multidft}
\caption{Fourier Transforms of GD358 for the 2010, 2011, and 2014 observing seasons.
The frequency range of the observed series of $\ell=1$ modes discussed in Section \ref{analysis} 
is indicated by the left arrow (red).  Peaks below $\approx$ 2400 \muHz\ are combination 
frequencies discussed in Section \ref{analysis} (right arrow, blue). 
(A color version of this figure is available in the online journal.)
\label{fts}
}
\end{figure}

@@

Perusal of Tables \ref{freq1} and \ref{freq2} shows that GD358's observed frequencies vary in two
important ways.  First, frequencies detected in a given observing season are not found 
in all observing seasons. Asteroseismology is based on the assumption that the available pulsation
frequencies are linked to stellar structure.  Since we are fairly certain that GD358's internal structure 
does not change on the timescales of the observations, we can assume that GD358 excites 
different subsets of its available pulsations at different times. While this is a common phenomenon
seen in white dwarf pulsators, the selection mechanism remains mysterious. The best way to 
determine GD358's complete set of pulsation frequencies is to combine frequency identifications 
from multiple observing seasons as outlined in \citet{Kleinman98}.

\begin{figure}
\epsscale{0.8}
%\plottwo{gd358multif_2015.eps}{gd358multi.eps}
%\centering{
%\includegraphics[width=1.0]{gd358multif_2015.eps}
%}
\plotone{gd358multif_2015.eps}
\caption{A schematic representation of GD358's pulsation modes for all available data between
1982 and 2015. Systematic patterns of distribution are evident. The bands between 2400 and 1000
\muHz\ (400 and 1000 s) are of particular importance for this work. (A color version of this 
figure is available in the online journal.)
\label{schematic}
}
\end{figure}

Figure~\ref{schematic} presents a schematic representation of GD358's pulsation frequencies for all the 
available data. The features of asteroseismic importance are the localized bands between 900 and 2400
\muHz\ (1100 and 400 s). We interpret each band to represent a single radial overtone. The bands
themselves illustrate the second way in which GD358's frequencies vary. Each band consists of 
frequency detections from multiple observing seasons, but each band is significantly wider in 
frequency space than the frequency error of any single measurement, arguing that some process 
is acting on the frequencies. The simplest explanation is rotational splitting.  However, with the 
exception of the two highest frequency (shortest period) bands ($k=8$ and $k=9$ 
from \citet{Provencal09}), we find no clear evidence of multiplet structure in the frequency 
distributions of the lower frequency (longer period) bands. The lower frequency band widths are 
most likely the result of amplitude and/or frequency modulation that obscures any underlying 
signatures of rotational splitting.

\begin{figure}
 \epsscale{1.0}
 \plotone{gd358k17_k8.eps}
% \plottwo{gd358multifk17.eps}{gd358multifk8.eps}
 \caption{The detailed schematic distribution of frequencies for the bands near 1300({\em{right}}
 and 2360 \muHz\ ({\em{left}}). The 1300 \muHz\ band shows no multiplet structure, unlike the 2360 \muHz\
 band. Here we see clear evidence of multiplet structure. Assuming the triplet structure represents
 $\ell=1$, this implies a rotation period of $\approx 1.5$ days. Note changes in the scale for both axes.
 (A color version of this figure is available in the online journal.)
 \label{rot}}
\end{figure}

Figure \ref{schematic} also shows that the widths of the bands is not constant, but changes from band to band.
\citet{Bell15} presents an interesting analysis of the hydrogen atmosphere pulsator (DAV) KIC4552982, 
in which they identify 17 bands of pulsation frequencies. This DAV follows the general pattern exhibited 
by GD358: the highest frequency (shortest period) mode shows evidence of rotational splitting, while the 
lower frequency (longer period) modes are complex bands. The authors note that this DAV's bands have 
different widths in frequency space, and that there may be astronomical significance to this. Although the 
observational timebases and coverage are quite different (20 continuous months for KIC4552982 vs 30 
incomplete years for GD358), our data presents the opportunity to investigate this for a DB pulsator.  
We measured the width of each of GD358's band. We define ''width'' as the difference between the 
lowest and highest frequency detected in each band. Figure \ref{thick} presents the results. 
The widths of GD358's bands are commensurate with those found in KIC4552982.  We also find a general 
increase in width with decreasing frequency (increasing period), until we reach 
the mode at 1238\muHz\ (807 s). This band has a width at least twice as wide as any other.  What 
is different about this mode???

@@

GD358's combination frequencies provide a tool by which we can bolster $\ell$ identifications. 
Combination frequencies are typically observed in the FTs of moderate to large amplitude pulsators.  
They are identified by their exact numerical relationships with parent frequencies.  
The combinations themselves are not independent, but result from nonlinear effects associated 
with the surface convection zone \citep{Brickhill92, Brassard95, Wu01, Ising01}.  
\citet{Wu01} lays the groundwork, showing that observed amplitudes of the combination 
frequencies depend on geometric factors such as the $(\ell,m)$ indices of the parents and the 
inclination of the pulsation axis to the line of sight.

@@

Figure~\ref{modeamps} shows the resulting probability distribution of $\ell$ and $m$ values for the 1735.96 \muHz\
frequency as detected in 2014.

\begin{figure}
 \epsscale{0.8}
 \plotone{modeamps.eps}
 \caption{Probability distribution (from 0 to 1) of $\ell$ and $m$ values for the 1735.96 variation detected in 
 2014.  The solutions are from individual simulations with $Res_{rms}<9.5^{-06}$. The amplitudes of the 
 observed combination frequencies argue that this is $\ell=1$, $m$=1.  
 \label{modeamps}
 }
\end{figure}

Add table with all l,m ids

@@

\section{Asteroseismic fitting}
\label{fitting}

@@

@@

\begin{deluxetable}{llrrr}
\tablecolumns{5}
\tabletypesize{\small}
\tablewidth{0pc}
\tablecaption{}
\tablehead{
\colhead{Run Name} & \colhead{Telescope} & \colhead{Detector} & \colhead{Date} & \colhead{Length}\\
\colhead{} & \colhead{} & \colhead{} & \colhead{} & \colhead{(hrs)}
\label{journal}}
\startdata
\input{journaldata.tex}
\enddata
\end{deluxetable}

@@

\input{1982freq.tex}
\clearpage
\input{2011freq.tex}
\clearpage
\input{gd358fit.tex} % label is gd358freq
\clearpage
\input{fitt1} % label is fitt1
\clearpage
%\begin{thebibliography}{}
%\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
